\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-11-08 k-planar.tex
last three referee comments

\begin{proof}
Let $G$ be a $1$-plane multigraph. We may assume that no two edges incident to a common vertex of $G$ cross, since such a crossing can be removed by a local modification to obtain an isomorphic 1-plane graph in which the two edges do not cross\footnote{While this is true for 1-plane graphs it is not true for $k$-plane graphs with $k\ge 3$; the uncrossing operation can increase the number of crossings on a particular edge from $k$ to $2(k-1)$.}. We make $G$ into an \defin{edge-maximal} $1$-plane multigraph, by repeating the following operation:  If two vertices $v$ and $w$ of $G$ appear on a common face $F$ and there is no edge $vw\in E(G)$ contained in the boundary of $F$, then add the edge $vw$, embedded in the face $F$.  This may introduce parallel edges into $G$, but no two such edges  appear on the boundary of a common face.

\begin{figure}[h]
  \begin{center}
    \begin{tabular}{c@{\hspace{1cm}}c}
        \includegraphics{figs/one_planar_example-3} &
        \includegraphics{figs/one_planar_example-4} \\
        $G$ & $G_0$
     \end{tabular}
    \end{center}
    \caption{The graph $G_0$ obtained by removing pairs of crossing edges from $G$ is a plane multigraph whose faces all have three or four sides.}
    \label{one_planar_example}
\end{figure}

@@

If $W$ contains a dummy vertex $w_i$, then neither $w_{i-1}$ nor $w_{i+1}$ is a dummy vertex since if $w_{i-1}$ (respectively $w_{i+1}$) were a dummy vertex then the edge of $G$ that contains $w_{i-1}w_i$ (respectively $w_iw_{i+1}$) would be involved in at least two crossings.  Therefore each dummy vertex $w_i$ of $W$ is flanked by two non-dummy vertices $w_{i-1},w_{i+1}\in V(G)$.  Since $w_i$ has degree $4>1$ in $G'$ and no two edges incident to a common vertex cross each other, $w_{i-1}\neq w_{i+1}$.  Since $G$ is edge-maximal the edge $w_{i-1}w_{i+1}$ is an edge of $G$ on the boundary of $F$.  Therefore, if $F$ has a dummy vertex $w_i$ in its facial walk $W$, then $W=w_{i-1},w_i,w_{i+1}$ and $F$ is bounded by three edges of $G'$, each of which is contained in a different edge of $G$.

@@

\begin{proof}
Let $G_0$ be a graph embedded in the plane, with each face labelled a nation or a lake, and where each vertex of $G_0$ is incident with at most $d$ nations and let $G$ be the corresponding map graph.

@@

Let $G_1$ be a plane supergraph of $G_0^*$ obtained by adding the nation cycle of each face $F$ of $G_0$, and then triangulating each face with more than $d$ vertices on its boundary. $G_1$ is biconnected since $G^*_0$ is a biconnected spanning subgraph of $G_1$. Each nation cycle of length at least $3$ is now a facial cycle of $G_1$, and no face of $G_1$ has more than $d$ vertices on its boundary. Let $\widehat{G}_1$ be the $d$-framed graph whose frame is $G_1$.

>>>>

\begin{proof}
Let $G$ be a $1$-plane multigraph. We may assume that no two edges incident to a common vertex of $G$ cross, since such a crossing can be removed by a local modification to obtain an isomorphic 1-plane graph in which the two edges do not cross\footnote{While this is true for 1-plane graphs it is not true for $k$-plane graphs with $k\ge 3$; the uncrossing operation can increase the number of crossings on a particular edge from $k$ to $2(k-1)$.}. We make $G$ into an \defin{edge-maximal} $1$-plane multigraph, by repeating the following operation:  If two vertices $v$ and $w$ of $G$ appear on a common face $F$ and there is no edge $vw\in E(G)$ contained in the boundary of $F$, then add the edge $vw$, embedded in the face $F$.  This may introduce parallel edges into $G$, but no two such edges  appear on the boundary of a common face. 
\note{DW}{Add ``So each face is bounded by a triangle, and this process terminates by Euler's formula.''}

\note{DW}{I think $G_0$ should be replaced by $G'$ throughout this proof.}

\begin{figure}[!h]
	\begin{center}
		\begin{tabular}{c@{\hspace{1cm}}c}
			\includegraphics{figs/one_planar_example-3} &
			\includegraphics{figs/one_planar_example-4} \\
			$G$ & $G_0$
		\end{tabular}
	\end{center}
	\caption{The graph $G_0$ obtained by removing pairs of crossing edges from $G$ is a plane multigraph whose faces all have three or four sides.}
	\label{one_planar_example}
\end{figure}

@@

If $W$ contains a dummy vertex $w_i$, then neither $w_{i-1}$ nor $w_{i+1}$ is a dummy vertex since if $w_{i-1}$ (respectively $w_{i+1}$) were a dummy vertex then the edge of $G$ that contains $w_{i-1}w_i$ (respectively $w_iw_{i+1}$) would be involved in at least two crossings.  Therefore each dummy vertex $w_i$ of $W$ is flanked by two non-dummy vertices $w_{i-1},w_{i+1}\in V(G)$.  Since $w_i$ has degree $4>1$ in $G'$ and no two edges incident to a common vertex cross each other, $w_{i-1}\neq w_{i+1}$.  Since $G$ is edge-maximal, the edge $w_{i-1}w_{i+1}$ is an edge of $G$ on the boundary of $F$.  Therefore, if $F$ has a dummy vertex $w_i$ in its facial walk $W$, then $W=w_{i-1},w_i,w_{i+1}$ and $F$ is bounded by three edges of $G'$, each of which is contained in a different edge of $G$.

\note{DW}{Put \cref{one_planar_example} here?}

@@

\begin{proof}
Let $G_0$ be a graph embedded in the plane, with each face labelled a nation or a lake, and where each vertex of $G_0$ is incident with at most $d$ nations. Let $G$ be the corresponding map graph.

@@

Let $G_1$ be a plane supergraph of $G_0^*$ obtained by adding the nation cycle of each face $F$ of $G_0$, and then triangulating each face with more than $d$ vertices on its boundary. $G_1$ is biconnected since $G^*_0$ is a biconnected spanning subgraph of $G_1$. Each nation cycle of length at least $3$ is now a facial cycle of $G_1$, and no face of $G_1$ has more than $d$ vertices on its boundary. Let $\widehat{G}_1$ be the \note{DW}{Add ``edge-maximal''. Do we need to write this anywhere else?} $d$-framed graph whose frame is $G_1$.

### 2022-11-08 response2.tex
last three referee comments

\begin{response}
  We have added a footnote here explaining that the proof of Sperner's Lemma is based on a certain graph defined on the faces of the embedding (triangles plus outer face).  It relies only on the fact that the number of odd-degree vertices in this graph is even, which is true even if this graph is not simple.
\end{response}

@@

\begin{response}
  As part of addressing the referee's primary comment, we have introduced an extra claim that which shows that, for any $v\in V(G)$, there is a path in $H$ from $v$ to $a(v)$ of length at most $k-1$ in which $v$ participates in every vertex on this path, including $a(v)$.  We have rephrased this confusing sentence and replaced it with a reference to this claim.
\end{response}

@@

8. page 16, line 8. I would not call these “BFS spanning forests rooted
at V0” since they need not be BFS spanning forests (unless the same
terminology has already appeared elsewhere?).

@@

12. page 17, top. In the first two cases there may not be a vertex v3 defined
as we could have p = 2.

@@

@@

@@

>>>>

\begin{response}
  We have added a footnote here explaining that the proof of Sperner's Lemma is based on a certain graph defined on the faces of the embedding (triangles plus outer-face).  It relies only on the fact that the number of odd-degree vertices in this graph is even, which is true even if this graph is not simple.
\end{response}

@@

\begin{response}
  As part of addressing the referee's primary comment, we have introduced an extra claim which shows that, for any $v\in V(G)$, there is a path in $H$ from $v$ to $a(v)$ of length at most $k-1$ in which $v$ participates in every vertex on this path, including $a(v)$.  We have rephrased this confusing sentence and replaced it with a reference to this claim.
\end{response}

@@

8. page 16, line 8. I would not call these “BFS spanning forests rooted
at $V_0$” since they need not be BFS spanning forests (unless the same
terminology has already appeared elsewhere?).

@@

12. page 17, top. In the first two cases there may not be a vertex $v_3$ defined
as we could have $p=2$.

@@

\textcolor{orange}{DW: I have suggested a sentence to add. }

@@

\textcolor{orange}{DW: I think $G_0$ should be replaced by $G'$ throughout this proof.}

@@

\textcolor{orange}{DW: First point fixed. I have suggested words to add. }
